The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
fixed typo

		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle router which forwards the data to the exit router.

@@

			\item Some Tor users put more traffic on the network than they contribute by running a Onion Router. This means that these users are slowing the network down as they use more traffic than giving back. A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.

>>>>

		The first router in a circuit is the entrance router. The entrance router sends the data to one of the middle routers which forwards the data to the exit router.

@@

			\item Some Tor users put more traffic on the network than they contribute by running an Onion Router. This means that these users are slowing the network down as they use more traffic than giving back. A possible solution for this is to throttle certain high-bandwidth protocols such as BitTorrent at exit nodes or at Onion Proxies.
